\Section{Algebra practice---solving quadratic equations}

\begin{multicols}{2}

 Quadratic equations can have zero, one, or two real solutions.
 (We won't be using complex number solutions in this course.)
 You can solve quadratic equations by factoring or using the quadratic formula.
 Always put the equation in standard form before trying to solve it.
 Factoring is usually easier, but it requires some trial \& error and it doesn't always work.
 The quadratic formula always works (even if the equation factors), but there are many opportunities to make mistakes while using it.
 If there's no degree 1 term, you can solve by inverse operations (peeling the onion) but factoring and the quadratic formula work as well.

 Solve these equations using whatever method you like.
 If an equation has only complex solutions, just write ``no real solutions.''

 \columnbreak

 \begin{FormulaBox}{Quadratic formula}
  The solutions to a quadratic equation in standard form
  \begin{equation*}
   a x^2 + b x + c = 0
  \end{equation*}
  are
  \begin{equation*}
   \frac{
    -b \pm \sqrt{b^2 - 4 a c}
   }{
    2 a
   }
  \end{equation*}
  If the part under the root symbol $b^2 - 4ac$ comes out negative, there are no real solutions.
 \end{FormulaBox}
\end{multicols}

\begin{multicols}{2}
 \begin{ProblemSet}[pencil space=2.5in]
  \EqProb{x^2 + 4x + 3 = 0}
  \EqProb{x^2 - x + 6 = 0}
  \EqProb{-2 x^2 + 6 x + 3 = 0}
  \EqProb{3 x^2 - 4x = 0}
  \EqProb{x \cdot (x + 4) = 8 - x}
  \EqProb[pencil space=3.5in]{u^2 - 5 u + 6 = -2 u^2 + 2 u - 1}
 \end{ProblemSet}
\end{multicols}

Solve, giving decimal approximations to the nearest thousandth, as in 0.123 or 1.234.

\begin{ProblemSet}[pencil space=3in]
 \EqProb{0.2 x^2 - 3.7 x + 1.2 = 0}
\end{ProblemSet}

\newpage
\Subheading{Extra practice}

Solve these in the same way.

\begin{multicols}{2}
 \begin{ProblemSet}[pencil space=0in]
  \EqProb{x^2 + 2x + 1 = 0}
  \EqProb{x^2 - 2x - 1 = 0}
  \EqProb{x^2 - x + 3 = 0}
  \EqProb{x^2 - x - 3 = 0}
  \EqProb{x^2 + x + 6 = 0}
  \EqProb{x^2 + 5 x + 6 = 0}
  \EqProb{x^2 - 5x + 6 = 0}
  \EqProb{x^2 + x - 12 = 0}
  \EqProb{x^2 + x + 12 = 0}
  \EqProb{x^2 + 8x + 15 = 0}
  \EqProb{2 x^2 + 4 x + 2 = 0}
  \EqProb{2 x^2 + 6 x + 3 = 0}
  \EqProb{2 x^2 + 6 x - 3 = 0}
  \EqProb{2 x^2 - 6 x + 3 = 0}
  \EqProb{x^2 - 1 = 0}
  \EqProb{x^2 + 1 = 0}
  \EqProb{5 x^2 - 2 = 0}
  \EqProb{-2x^2 - 8x = 0}
  \EqProb{x^2 + 1 = 2x}
  \EqProb{-t^2 + 3t = 4}
  \EqProb{r^2 + 5r + 6 = 4}
  \EqProb{-7w + 6 = -2w^2 + 3}
  \EqProb{-0.01 x^2 + 5.25 x - 48.5 = 0}
  \EqProb{\frac{1}{x} + \frac{1}{x + 1} = 2}
 \end{ProblemSet}
\end{multicols}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "Business-calculus-workbook"
%%% End:
