\Section{Applications---rate of change}

You are traveling north on I-95 from Savannah.
After an early lunch, you drive at a constant speed, so that at noon, you are at mile marker 15.
At 12:30, you reach mile marker 50.

\begin{ProblemSet}
 \begin{Problem}[pencil space=0in]
  Plot your location, that is, the mile marker on I-95, as a function of time on this grid.
  Represent time as the number of hours since noon.
  Let time go up to at least 3:00.
  Be sure to label the axes and indicate the time scale and location scale.

  \bigskip
  \GraphingGridSmall

 \end{Problem}
 \begin{Problem}
  Since your speed is constant, your location $y$ is a linear function of time $t$.
  Write an equation $y = m t + b$ for your location as a function of time.
 \end{Problem}
 \begin{Problem}[pencil space=0.5in]
  What is your speed during this trip?
  What feature of the equation $y = m t + b$ does this number correspond to?
 \end{Problem}
 \begin{Problem}[pencil space=0.5in]
  At what time will you arrive at mile marker 190?
 \end{Problem}
\end{ProblemSet}

\newpage
The water level in a tidal creek is approximately
\begin{equation*}
 w(t) = 3 + 1.2 t - 0.08 t^2 \text{ feet}
\end{equation*}
where $t$ is time in hours from now.

\begin{ProblemSet}[pencil space=2in]
 \begin{Problem}
  What is the derivative of the water level as a function of time?
 \end{Problem}
 \begin{Problem}
  What will the water level be $4$ hours from now?
  Give your answer to the nearest thousandth.
 \end{Problem}
 \begin{Problem}
  What will the water level be $4.5$ hours from now?
  Give your answer to the nearest thousandth.
 \end{Problem}
 \begin{Problem}
  What is the \emph{average rate of change} of the water level over the time interval from $4$ to $4.5$ hours from now?
  Give your answer to the nearest thousandth.
 \end{Problem}
 \begin{Problem}
  At what \emph{instantaneous rate} with respect to time will the water level be changing $4$ hours from now?
  Give your answer to the nearest thousandth.
 \end{Problem}
\end{ProblemSet}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "Business-calculus-workbook"
%%% End:
